### 2016-02-12 Manuscript/BiologyLetters/medianSummary.tex
My attempt
Feel free to revert, I tried to make it more media friendly

%What's the story
To understand changes of biodiversity, it is crucial to combine both living and fossil species in the same analysis.
We can do so by using the DNA from living species and enough anatomical data in common between living and fossil species.
%What we found
In this study we found that only a small amount of living mammals have available anatomical data and that this could be a problem for combining them with fossils.
%How's that gonna solve the world
We suggest that an increase in sampling effort in natural history museum collections, where this data lies, is necessary to efficiently combine living and fossil species in the same analysis.

>>>>

Scientists use family trees to understand changes in biodiversity through time. But the trees often only use living species, ignoring extinct groups like mammoths. Therefore we must place living and 
extinct species in the same trees. We can do so using the DNA from living species and anatomical data from living and extinct species. However, we found that few living mammals have enough available anatomical data to determine how they are related to extinct species. We suggest that we must collect more anatomical data from living species in museum collections to efficiently create family trees of living and extinct species.
